Nested Sampling with Multiple Objective Functions

### 2018-06-20 doc/ms.tex
Fixes

    Set $(T_1, T_2)$, the temperatures of a canonical distribution of interest \\
    Compute $\hat{Z}(T_1, T_2) \leftarrow \sum_{ij} w_{ij}\left(L_1(\xx_{ij})/T_1 + L_2(\xx_{ij})/T_2\right) / \sum_{ij} w_{ij}$\\
  \vspace*{0.5em}
  \caption{The `Switch Sampling' algorithm.}
\end{algorithm}

>>>>

    Set $(T_1, T_2)$, the temperatures of a canonical distribution of interest \\
    Compute $\hat{Z}(T_1, T_2) \leftarrow \left(\sum_{ij} w_{ij}L_1(\xx_{ij})^{1/T_1}L_2(\xx_{ij})^{1/T_2}\right) / \sum_{ij} w_{ij}$\\
  \vspace*{0.5em}
  \caption{The `Switch Sampling' algorithm.}
\end{algorithm}
